Fourmile

### 2022-09-01 fourmile_dataprocess.Rmd
comparing niwot snotel vs niwot prism pixel

>>>>

## Compare Niwot SNOTEL pirecip to prism pixel

```{r}
niwot_prism <- read_csv(here('data', 'niwot_prism_compare.csv'))

ni_prism <- niwot_prism %>%
  filter(!row_number() %in% c(1:10)) %>%
  rename(date = 1,
         prism_mm = 2) %>%
  mutate(date = ymd(date))

niwot_snotel <- prec_update %>%
  dplyr::select(c(date, Niwot_Snotel)) %>%
  rename(snotel_mm = Niwot_Snotel)

niwot_compare <- full_join(ni_prism, niwot_snotel, by = 'date')

niwot_compare <- niwot_compare %>%
  mutate(diff_mm = snotel_mm - prism_mm)

summary(niwot_compare$diff_mm)
count(niwot_compare)

#filter to look at sept - june
```
